### 2020-05-16 paper.tex
Reactive Inspector

\section{Discussion}
\label{sec:discussion}

@@

\begin{itemize}
	\item Informal interviews/war stories only
	\begin{itemize}
		\item Describe background of interview partners
		\item Frontend engineering heavy
	\end{itemize}
\end{itemize}

>>>>

\section{Discussion of Previous Efforts}
\label{sec:discussion}

Our work is not the first approach on understanding and improving on the struggles software engineers face when working on RP code, no matter of using RxJS or not. We are going to present academic as well as non-academic efforts which contributed in the field of RP debugging in the past.

\subsection{Reactive Inspector}

Salvaneschi et al. did focus their research heavily on RP during the mid 2010s. Beside the creation of REScala in 2014 \cite{REScala}, an RP DSL and runtime for the Scala programming language, they looked into the debugging habits of software engineers as well. In the paper ``Debugging for Reactive Programming'' \cite{positiveEffectsRP}, Salvaneschi et al. elaborate on the necessity of RP debugging tools which can understand the specific language abstractions. With the plugin \emph{Reactive Inspector} \footnote{\url{http://guidosalva.github.io/reactive-inspector/}} for the Eclipse IDE, they provide a debugger which understands the RP language abstractions of REScala. One of its main features is the visualization of the internal dependency graph. The new class of  breakpoints, the ``reactive breakpoints'', builds upon the visualized graph as well: They do not depend on a specific line of code or statement rather then on a specific node in the graph. The execution of the program can be interrupted e.g. once a node retains a specific output value or an event of interest takes place in the runtime. Along with the RP specific debugging features, \emph{Reactive Inspector} implements omniscient debugging concepts as well: Time travel allows to record and replay runtime behavior at any time.

\begin{itemize}
	\item Visualization of the graph
	\item Omniscient

Herman Benken \cite{rxfiddle}

rxspy-js

@@

\begin{itemize}
	\item Informal interviews/war stories only
	\begin{itemize}
		\item Describe background of interview partners
		\item Only 4 Participants in experiment
		\item Code in experiment carefully crafted... Though is it representative?
		\
	\end{itemize}
\end{itemize}
